Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-09 paper/paper.tex
updated Table II
updated table III
minor fix

\begin{itemize}
\item Released latest version after Jan 1, 2018
\item Contains more than 1K starts, if on GitHub  
\item Uses a public issue tracker
\end{itemize}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{3}{c}{\# JS files} \\
    \cline{3-5}
                               &         & original & compile-in-all &  no-fail-in-all \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
    29,846 & - \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,021 & -\\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & -\\
    \veight{} & \cite{v8} & 75 & 57 & -\\
    \midrule    
    Duktape & \cite{duktape} & 1,195 & 921 & -\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & -\\
    JSI & \cite{jsi} & 99 & 63 & -\\
    Tiny-js & \cite{tinyjs} & 49 & 37 & -\\    
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesFilter{} & -\\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \midrule
    \jsc{} & - & - & - & - & - & - & - \\
    \veight{} & - & - & - & - & - & - & - \\
    \chakra{} & - & - & - & - & - & - & - \\
    \smonkey{} & - & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

>>>>

\begin{itemize}
\item Released latest version after Jan 1, 2018
\item Contains more than 1K stars on GitHub  
\item Uses a public issue tracker
\end{itemize}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{3}{c}{\# JS files} \\
    \cline{3-5}
                               &         & original & compile-in-all &  no-fail-in-all \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
    29,846 & 18,943 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 37 & 37\\
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \midrule
    \jsc{} & 4330 & 4330 & 4330 & - & - & - & - \\
    \veight{} & 3404 & 3404 & 3401 & - & - & - & - \\
    \chakra{} & 9104 & 9104 & 9104 & - & - & - & - \\
    \smonkey{} & 3943 & 3943 & 3943 & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}
